---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


<!-- README.md is generated from README.Rmd. Please edit that file -->




[![Build Status](https://travis-ci.org/vincenzocoia/powers.svg?branch=master)](https://travis-ci.org/vincenzocoia/powers)

__Note__: This R package is not mean to be "serious". It's just for homework purposes. 

# powers

This is an R package that gives the power of a vector of numbers. The functions contained in this package include: 

    1. `square()` function: squares a vector of numbers
    2. `reciprocal()` function: computed `1/x`, where `x` is a vector of numbers
    3. `cube()` function: raise a vector of numbers to power 3
    4. `Box_Cox()` function: compute Box-Cox transformation of a vector


## Installation

You can install powers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("vincenzocoia/powers")
```

## Example

See the vignette for more extensive use, but here's an example:

```{r example1}
powers::square(3)
```

```{r example2}
powers::cube(4)
```


```{r example3}
powers::reciprocal(5)
```

```{r example4}
vec <- c(2,3,4,2)
powers::Box_Cox(vec,2)
```
## For Developers

Use the internal `pow` function as the machinery for the front-end
functions such as `square`, `cube`, and `reciprocal`. Although, the `Box_Cox` function is independent of the power function

